Model \& Simulation of South Bend Government Call Center using Arena

### 2018-12-04 Paper.tex
added other results

@@

Secondly, the self-serve simulation experiment shows that operator utilization decreases in a linear fashion depending on the number of callers who can and do choose the self-service option, all else held equal.  Similarly, wait time and queue length decrease as well.  As expected, a self-serve option that even a small percentage of customers use could clearly make the case for removing one operator (as supported above, even without a self-serve option).  However, the true effectiveness of adding such a system would take into other factors, such as start-up and maintenance costs and customer education and marketing.

@@

Both of these experiments include estimated parameters, particularly the hypothetical self-service model.  As a result, neither of these experiments definitively answer/attempt to answer any of these question until they are compared to internal data for accuracy.  Such data would replace estimates with more accurate numbers and distributions; then, a simulation could be run for a definitive question.

>>>>

	The theorized 67\% utilization rate for the self-service option was then explored with an increase in mean call arrivals.  Through this analysis, it was observed that the self-service model with approximately a 20\% increase in total call arrivals exhibits agent utilization levels in range of the current state (base model) of the call center without the self-service option ($\approx$ 40\%).

@@

Secondly, the self-serve simulation experiment shows that operator utilization decreases in a linear fashion depending on the number of callers who can and do choose the self-service option, all else held equal.  Similarly, wait time and queue length decrease as well.  As expected, a self-serve option that even a small percentage of customers use could clearly make the case for removing one operator (as supported above, even without a self-serve option).  However, the true effectiveness of adding such a system would take into other factors, such as start-up and maintenance costs and customer education and marketing.  The extension of the self-service model analysis shows the increased amount of volume the call center can handle without necessitating hiring more staff.  Depending on the city's forecasts for the center, this may be a convincing argument to add this self-service system.

@@

Both of these experiments include estimated parameters, particularly the hypothetical self-service model.  As a result, neither of these experiments definitively answer/attempt to answer any of these questions until they are compared to internal data for accuracy.  Such data would replace estimates with more accurate numbers and distributions; then, a simulation could be run for a definitive question.
